---
title: "Mgrtibbles"
---

__mgrtibbles__ is a R package containing various datasets in __tibbles__.
They were curated into a R package by [Matthew Gemmell](https://m-gemmell.github.io/).

For full information please see the [mgrtibbles github page](https://github.com/m-gemmell/mgrtibbles/tree/main)

## Install and load

Installation and loading instruction below:

You will need the `remotes` package installed and loaded.

```{r, eval=FALSE}
install.packages("remotes")
library(remotes)
```

```{r, eval=FALSE}
remotes::install_github("m-gemmell/mgrtibbles")
library(mgrtibbles)
```

## Accessing data

Once you have installed and loaded the package you can access one of the various datasets as a [__tibble__](/tibble/tibble.qmd) like below:

```{r}
mgrtibbles::mammal_sleep_tbl
```

To see the format and variable description use `?`.
For example:

```{r, eval=FALSE}
?mgrtibbles::crab_age_pred_tbl
```

## Tibble details

[amphibian_div_tbl details](https://github.com/m-gemmell/mgrtibbles/wiki/amphibian_div_tbl)

[bat_roost_tbl details](https://github.com/m-gemmell/mgrtibbles/wiki/bat_roost_tbl)

[crab_age_pred_tbl details](https://github.com/m-gemmell/mgrtibbles/wiki/crab_age_pred_tbl)

[crop_and_soil_tbl details](https://github.com/m-gemmell/mgrtibbles/wiki/crop_and_soil_tbl)

[fisheries_long_tbl details](https://github.com/m-gemmell/mgrtibbles/wiki/fisheries_long_tbl)

[fisheries_wide_tbl details](https://github.com/m-gemmell/mgrtibbles/wiki/fisheries_wide_tbl)

[mammal_sleep_tbl details](https://github.com/m-gemmell/mgrtibbles/wiki/mammal_sleep_tbl)

[mushroom_tbl details](https://github.com/m-gemmell/mgrtibbles/wiki/mushroom_tbl)